Finiteness in Cubical Type Theory

### 2020-01-17 paper.tex
categories etc

That is the first thing this paper sets out to investigate: different finiteness
predicates.
The five in particular that we are interested in are organised in
figure~\ref{finite-classification}.
We especially want to examine what separates each predicate: what extra
information do you need, for instance, to go from a proof of Cardinal finiteness
(section~\ref{cardinal}) to manifest Bishop finiteness
(section~\ref{manifest-bishop}).
These predicates aren't just different in proof obligation, either: there are
concrete types which can be shown to satisfy some, but not all, of these
finiteness predicates.

@@

Next, we will examine the category-theoretic and topos-theoretic interpretations
of each of the predicates.

>>>>

That is the first thing this paper sets out to investigate: different finiteness
predicates.
The five in particular that we are interested in are organised in
figure~\ref{finite-classification}.
We especially want to examine what separates each predicate: what extra
information do you need, for instance, to go from a proof of Cardinal finiteness
(section~\ref{cardinal}) to manifest Bishop finiteness
(section~\ref{manifest-bishop}).

@@

Next, we will examine the category-theoretic and topos-theoretic interpretations
of each of the predicates.
We will give a ``category of finite sets'' for each finiteness predicate, and
then prove the various closure properties required to arrive at the relevant
topos (we show that decidable Kuratowski finite sets form a \(\Pi\)-pretopos,
for instance).
